Title?

### 2016-09-30 draft.tex
added results

\section{Computational details}
	simple energy loss calculation

@@

The calculation of these diagrams is straightforward, and is described in the appendix. Having obtained the diagrams the calculation diverges from the axion bremsstrahlung calculation, since in the kinematic region of interest for supernova explosions the mass of the $A'$ boson is not necessarily negligible. The kinematic relations are thus \bea 
p_1 \cdot p_2 &=& M_N^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot q_a,\\
p_1 \cdot p_3 &=& M_N^2 + k \cdot l - \frac{k^2}{2} + p_3 \cdot q_a,\\  
p_1 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2}{2} + p_4 \cdot q_a, \\
p_2 \cdot p_3 &=& M_N^2 - \frac{l^2}{2}, \\ 
p_2 \cdot p_4 &=& M_N^2 - \frac{k^2}{2},\\
p_3 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2 + k^2}{2}.
\eea
Unfortunately, with these relations it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression for the spin-averaged squared matrix element, $ \mathcal{M}^2_{pp}$, contains some two hundred and fifty terms, and thus we do not reproduce that result here.\footnote{At this point we diverge from Ref.~\cite{Dent:2012mx} for two reasons.  One, they use the kinematics as if the $A'$ were massless, as in the axion calculation, and independent of that choice, their squared matrix element does not respect the correct exchange symmetry, as can be seen by inspection of their Eq. (A.3), with their claim that only the coefficient $C_k$ appearing in that equation is nonzero.}

 For the $pn$ scattering, the calculation proceeds similarly, with the only new Feynman diagram coming from bremsstrahlung off the internal pi, resulting in  
 \beq
 M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
 	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \varepsilon
\eeq
Again, due to the more complicated kinematics due to the non-negligible mass of the $A'$, the resulting squared amplitude, $ \mathcal{M}^2_{pn}$, is too unwieldy to reproduce here.

@@

The actual quantity of interest therefore is the rate of energy emission through dark bosons. From the spin-summed squared amplitudes already given, this is obtained by integrating over the phase space, and adding a factor of energy
\beq
Q_i = \int (2\pi)^4 E_A \sum_{spins} \mathcal{M}^2_i f(p_1) f(p_2)\delta(p_1+p_2-p_3-p_4-q_a) d\Pi,
\eeq
where $d\Pi$ is the Lorentz-invariant phase space, $ E_A $ is the energy of the emitted boson, and $ f(p) $ are the initial occupation numbers. The nucleons in the core are comfortably non-degenerate and non-relativistic, so  the Pauli blocking factor is omitted and the Maxwell-Boltzmann distribution is used  
\beq
f(p) =  \frac{n_b}{2} (\frac{2 \pi}{M_N T})^{3/2} e^{-\frac{\textbf{p}^2} {2 M_N T}}.
\eeq

@@

\subsection{Trapping limit}
The second constraint that produces an upper bound on the excluded region comes from considering trapping of dark bosons within the supernova. With a large enough coupling, the new particles will thermalize and then they will be emitted from a spherical shell.  In this case the luminosity is given simply by the Steffan-Boltzmann law
\beq
\mathcal{L}_t  = 4\pi r^2 T_A^4 \sigma,
\eeq
where $ r $ is now the radius of the emitting shell and $ T_A $ its temperature. We can estimate $ r = 10$ km, since the density of the supernova drops drastically around that point. After taking that value for r, the bound on the luminosity translates into a bound on $ T_A $ 
\beq
T_A \le 9.586\rm\ MeV.
\eeq
That bound can then be translated into the desired bound on the coupling as a function of mass by assuming that the particles are emitted from an optical depth $ \tau = 2/3 $, and finding the temperature that corresponds to that optical depth. This is a somewhat involved calculation.
First, one needs a model for the density and temperature in the supernova. Following \cite{Dent:2012mx}, we assume 
\bea
\rho &=& \rho_p \left(\frac{R}{r}\right)^n,\\
T &=& T_R \left(\frac{\rho(r)}{\rho_R}\right)^{1/3},
\eea
with $  \rho_p  = 3\times10^{14}\ {\rm g/cm}^3, T_R = 30$ MeV, and taking $ n = 5 $. The optical depth is given by 
\beq
\tau = \int_{r_x}^{\infty} \kappa \rho dr,
\eeq
where $ \kappa$ is the opacity.  To find the opacity, we start from the reduced mean Rosseland opacity 
\beq
\frac{1}{\kappa \rho} = \int_{m_x}^{\infty} \frac{15}{4 \pi^4 T^5} \frac{E_A^2 e^{E_A/T} \sqrt{E_A^2 - m_A^2}}{(e^{E_A/T}-1)^2} l_A dE_A,
\eeq
where $ l_A $ is the mean free path.

@@

\begin{figure}[h!]
\includegraphics[height=9cm]{ope_bound.eps}
\caption{CAPTION}
\end{figure}

Both approaches produce constraints that are significantly weaker than the previous work, and that largely reproduce constraints already obtained from beam dump experiments. The squared matrix element obtained from the full one-pion-exchange in the end agrees quite well with that obtained using the approximations appropriate for axionic calculations; the reduction in the bremsstrahlung rate apparently results from significant changes to the phase space when the exact kinematics are used. The effective field theory calculation weakens the constraint by a further order of magnitude, and this difference between the EFT and OPE constraints results only from a difference in the matrix element calculated from each. It's well-known that the OPE model ignores effects related to chiral symmetry, and these evidently serve to reduce the bremsstrahlung rate considerably. Although there is some question as to the applicability of the simple pionless EFT at the highest masses considered, but at that point even significant deviation would not change the overall conclusion.

\section{Discussion/Conclusion}

\appendix
\section{Bremsstrahlung diagrams}
	Each of the $p-p-\pi $ vertices contribute a factor of $g_{pp}$,  the pseudoscalar pion-nucleon coupling. $f_{pp}$, the pseudovector pion-nucleon coupling, is related by $g_{pp} = \frac{2M_N}{m_\pi} f_{pp} $. The $ p-p-A' $ vertex contributes $e\epsilon \gamma_\mu$, where $\epsilon$ is the mixing strength between the photon and dark photon. Labeling the contributions according to the Feynman diagrams in Fig. , the matrix elements are 
	\bea
	M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\varepsilon} u(p_1),\\
	M_2 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \varepsilon  u(p_1), \\
	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
	M_4 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
	M_6 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),\\
	M_8 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),
	\eea
	where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and the dark photon's polarization is given by $\varepsilon$. 
	For $pn$ scattering, four of the diagrams are simply the $ M_1, M_2, M_3, M_4 $ given above, with the only new Feynman diagram coming from bremsstrahlung off the internal pi, resulting in  
	 \beq
	 M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \varepsilon
	 \eeq
	 Note that these matrix elements agree with Ref.~\cite{Dent:2012mx}.
\acknowledgments

>>>>

\section{Computational details}

@@

The calculation of these diagrams is straightforward, and is described in the appendix. Having obtained the diagrams the calculation diverges from the axion bremsstrahlung calculation, since in the kinematic region of interest for supernova explosions the mass of the $A'$ boson is not necessarily negligible. The kinematic relations are thus \bea 
p_1 \cdot p_2 &=& M_N^2 - \frac{l^2}{2} - \frac{k^2}{2} + p_2 \cdot q_a,\\
p_1 \cdot p_3 &=& M_N^2 + k \cdot l - \frac{k^2}{2} + p_3 \cdot q_a,\\  
p_1 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2}{2} + p_4 \cdot q_a, \\
p_2 \cdot p_3 &=& M_N^2 - \frac{l^2}{2}, \\ 
p_2 \cdot p_4 &=& M_N^2 - \frac{k^2}{2},\\
p_3 \cdot p_4 &=& k \cdot l + M_N^2 - \frac{l^2 + k^2}{2}.
\eea
Unfortunately, with these relations it does not seem to be possible to simplify the amplitude into an analytically usable form without making unjustified approximations, and so the final expression for the spin-averaged squared matrix element, $ \mathcal{M}^2_{pp}$, contains some two hundred and fifty terms, and thus we do not reproduce that result here. The pn calculation likewise results in a very large and unwieldy expression for $ \mathcal{M}^2_{pn}$. \footnote{At this point we diverge from Ref.~\cite{Dent:2012mx} for two reasons.  One, they use the kinematics as if the $A'$ were massless, as in the axion calculation, and independent of that choice, their squared matrix element does not respect the correct exchange symmetry, as can be seen by inspection of their Eq. (A.3), with their claim that only the coefficient $C_k$ appearing in that equation is nonzero.}

@@

The actual quantity of interest therefore is the rate of energy emission through dark bosons. From the spin-summed squared amplitudes already found, this is obtained by integrating over the phase space, and adding a factor of energy of the emitted particle.
\beq
Q_i = \int (2\pi)^4 E_A \sum_{spins} \mathcal{M}^2_i f(p_1) f(p_2)\delta(p_1+p_2-p_3-p_4-q_a) d\Pi,
\eeq
where $d\Pi$ is the Lorentz-invariant phase space, $ E_A $ is the energy of the emitted boson, and $ f(p) $ are the initial occupation numbers. The nucleons in the core are comfortably non-degenerate and non-relativistic, so  the Pauli blocking factor is omitted and the Maxwell-Boltzmann distribution is used  
\beq
f(p) =  \frac{n_b}{2} (\frac{2 \pi}{M_N T})^{3/2} e^{-\frac{\textbf{p}^2} {2 M_N T}}.
\eeq

@@

\subsection{Trapping limit}
The second constraint that produces an upper bound on the excluded region comes from considering trapping of dark bosons within the supernova. With a large enough coupling, the new particles will thermalize and then will be emitted from a spherical shell.  In this case the luminosity is given simply by the Steffan-Boltzmann law
\beq
\mathcal{L}_t  = 4\pi r^2 T_A^4 \sigma,
\eeq
where $ r $ is now the radius of the emitting shell and $ T_A $ its temperature. We can estimate $ r = 10$ km, since the density of the supernova drops drastically around that point. After taking that value for r, the bound on the luminosity translates into a bound on $ T_A $ 
\beq
T_A \le 9.586\rm\ MeV.
\eeq
That bound can then be translated into the desired bound on the coupling as a function of mass by assuming that the particles are emitted from an optical depth $ \tau = 2/3 $, and finding the temperature that corresponds to that optical depth. This is a somewhat involved calculation.
First, one needs a model for the density and temperature in the supernova. Following \cite{Dent:2012mx}, we assume 
\bea
\rho &=& \rho_p \left(\frac{R}{r}\right)^n,\\
T &=& T_R \left(\frac{\rho(r)}{\rho_R}\right)^{1/3},
\eea
with $  \rho_p  = 3\times10^{14}\ {\rm g/cm}^3, T_R = 30$ MeV, and taking $ n = 5 $. The optical depth is given by 
\beq
\tau = \int_{r_x}^{\infty} \kappa \rho dr,
\eeq
where $ \kappa$ is the opacity.  To find the opacity, we start from the reduced mean Rosseland opacity 
\beq
\frac{1}{\kappa \rho} = \int_{m_x}^{\infty} \frac{15}{4 \pi^4 T^5} \frac{E_A^2 e^{E_A/T} \sqrt{E_A^2 - m_A^2}}{(e^{E_A/T}-1)^2} l_A dE_A,
\eeq
where $ l_A $ is the mean free path.

@@

\begin{figure}[h!]
\includegraphics[height=9cm]{stages.eps}
\caption{The changes in the bounds generated as each stage of the calculation departs from Ref.~\cite{Dent:2012mx}. Interestingly the kinematics have apparently relatively little effect.}
\end{figure}

\begin{figure}[h!]
	\includegraphics[height=9cm]{endtoend.png}
	\caption{A comparison of the final result for the excluded region with the result from Ref.~\cite{Dent:2012mx}. The excluded region is clearly significantly less restrictive, and opens up the region of parameter space for $\epsilon \approx  1e-8-9 $.}
\end{figure}

\section{Discussion/Conclusion}	
	The revised approach produce constraints that are significantly weaker than the previous work, and that largely reproduce constraints already obtained from beam dump experiments.

\appendix
\section{Bremsstrahlung diagrams}
	Each of the $p-p-\pi $ vertices contribute a factor of $g_{pp}$,  the pseudoscalar pion-nucleon coupling. $f_{pp}$, the pseudovector pion-nucleon coupling, is related by $g_{pp} = \frac{2M_N}{m_\pi} f_{pp} $. The $ p-p-A' $ vertex contributes $e\epsilon \gamma_\mu$, where $\epsilon$ is the mixing strength between the photon and dark photon. Labeling the contributions according to the Feynman diagrams in Fig. , the matrix elements are 
	\bea
	M_1 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed{\varepsilon} u(p_1),\\
	M_2 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_1} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p3) \gamma_5 (\slashed{p}_1 - q_a +M_N)\slashed \varepsilon  u(p_1), \\
	M_3 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
	M_4 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 - 2 q_a \cdot p_2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \gamma_5 (\slashed{p}_2 - q_a +M_N)\slashed \varepsilon  u(p_2), \\
	M_5 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p3) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
	M_6 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_3} \bar{u}(p_3) \gamma_5 u(p_1) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_3 + q_a +M_N)\gamma_5 u(p_2),\\
	M_7 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{l^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_3) \gamma_5 u(p_2) \bar{u}(p4) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),\\
	M_8 &=& \frac{4 M_N}{ m_\pi} \frac{f_{pp}^2 e \epsilon}{k^2-m_\pi^2
	}  \frac{1}{m_{A^\prime}^2 + 2 q_a \cdot p_4} \bar{u}(p_4) \gamma_5 u(p_2) \bar{u}(p_3) \slashed{\varepsilon} (\slashed{p}_4 + q_a +M_N)\gamma_5 u(p_1),
	\eea
	where the exchange momenta are defined by $ k = p_2-p_4 $ and $ l = p_2-p_3 $, and the dark photon's polarization is given by $\varepsilon$. 
	For $pn$ scattering, four of the diagrams are simply the same as those given above. The only new Feynman diagram comes from bremsstrahlung off the internal pion, and results in  
	 \beq
	 M'_5 = \frac{4 M_N}{ m_\pi} \frac{f_{pn}^2 e \epsilon}{l^2-m_\pi^2
	 }  \frac{1}{(l-q_a)^2 - m_\pi^2} \bar{u}(p_4) \gamma_5 u(p_1) \bar{u}(p_3) u(p_2) (q_a - 2l)\cdot \varepsilon
	 \eeq
	 Note that these matrix elements agree with Ref.~\cite{Dent:2012mx}.
\acknowledgments
